---
title: "SURVEY LIVESTOOK"
description: |
  Se presenta dos imagen interactivas que refieren al porcentaje de distribución pecuaria en el municipio de Entre Ríos - Cochabamba.

author:
  - name: Franklin Santos
    url: https://franklinsantos.com
    affiliation: Instituto Nacional de Innovación Agropecuaria y Forestal (INIAF) 
    orcid_id: 0000-0002-7509-2910
format: html
---

## Data Analysis

```{r}
#| warning: false
library(tidyverse)
library(googlesheets4)
```

```{r}
#| warning: false
data = read_sheet("https://docs.google.com/spreadsheets/d/1RTd05TLzWnjICRkXU_eMDJlNqdjePKfjE5XPu8K0VNg/edit?usp=sharing")


```

We are going to rename our interest variables and make a new data.

```{r}
datafs = data %>%
  rename(sindicatos = `Sindicato/predio`,
         investigacion = `Para mejorar su ganado, que se debería investigar?`,
         problemas = `Qué problemas tiene en su predio familiar?`,
         requerimiento = `Qué necesidades o soluciones requiere para la ganadería?`) %>%
  select(sindicatos, investigacion, problemas, requerimiento)
```

Now we will clean names of `sindicatos` column

```{r}
cleandata = datafs %>%
  mutate(sindicatos_clean = case_when(
    str_detect(sindicatos, "S[an|AN]") ~ "San Salvador",
    str_detect(sindicatos, "[M|m]arzo") ~ "23 de Marzo Ichoa",
    str_detect(sindicatos, "[L|l]auca") ~ "Lauca Bulo Bulo",
    str_detect(sindicatos, "[B|b]ulo") ~ "Lauca Bulo Bulo",
    str_detect(sindicatos, "[F|f][a|á]tima") ~ "Villa Fatima",
    str_detect(sindicatos, "[J|j]ulio") ~ "16 de Julio",
    str_detect(sindicatos, "[A|a]manecer") ~ "Nuevo Amanecer A",
    str_detect(sindicatos, "TUPAK") ~ "Tupak Katari",
    str_detect(sindicatos, "septiembre") ~ "Tupak Katari",
    str_detect(sindicatos, "Monte") ~ "Tupak Katari",
    str_detect(sindicatos, "[A|a]bril") ~ "25 de Abril",
               TRUE ~ as.character(sindicatos))) %>%
  relocate(sindicatos_clean)
  
cleandata %>%
  count(sindicatos_clean) %>%
  arrange(desc(n))
```


Now we are going to clean last three columns, because I need to build a word cloud picture. 

```{r}
words1 = cleandata %>%
  separate_rows(investigacion, sep = ",")


clean_invest =  words1 %>%
  mutate(investigacion_clean = case_when(
    str_detect(investigacion, "Adaptabilidad") ~ "Adaptabilidad animal",
    str_detect(investigacion, "pasturas") ~ "Mejoramiento de pastos",
    str_detect(investigacion, "pasto") ~ "Mejoramiento de pastos",
    str_detect(investigacion, "ración") ~ "Nutricion animal",
    str_detect(investigacion, "Nutrición") ~ "Nutricion animal",
               TRUE ~ as.character(investigacion))) %>%
  relocate(investigacion_clean, .after = investigacion) %>%
  select(sindicatos_clean, investigacion, investigacion_clean)

tableword = clean_invest %>%
  count(investigacion_clean)

```

```{r}
#| warning: false
library(highcharter)
hchart(
  tableword,
  "treemap",
  hcaes(investigacion_clean, value = n, colorValue = n),
  borderColor = NA #delete border
) %>%
  hc_colorAxis(stops = color_stops())%>%
  hc_title(text = "Para mejorar su ganado, que se debería investigar?")%>%
  hc_colorAxis(end0nTick = FALSE)
```


:::{.callout-note}
Note that there are five types of callouts, including:
`note`, `warning`, `important`, `tip`, and `caution`.
:::

:::{.callout-tip}
## Tip With Caption

This is an example of a callout with a caption.
:::

:::{.callout-caution collapse="true"}
## Expand To Learn About Collapse

This is an example of a 'folded' caution callout that can be expanded by the user. You can use `collapse="true"` to collapse it by default or `collapse="false"` to make a collapsible callout that is expanded by default.
:::












